MCC Predictions

### 2018-05-03 stats/ex3_comparisons.Rmd
weaker preference version

var pragmaticListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs);
observe(S1, utterance)
return {lexicon: lexiconName, obj: obj.shape == "circle" ? 1 : 0}
}})
}

@@

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors.priorProbs)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

  return {noisyModelPred: Math.exp(noisyModelPredictions.score(1)), noise: noise, Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment}

@@

 return conditionOutput
}

Infer({model: model, method: "MCMC", samples: 10})
'
```

@@

bda <- webppl(
  program_code = paste(rsaUtils, rsaModel2, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR"
)

jsonlite::toJSON(allConditions, pretty = T)

@@

>>>>

var pragmaticListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
}

@@

  //display(JSON.stringify(conditionSpecificData[0].correct_inf))

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]

@@

 return extend(_.fromPairs(conditionOutput), {noise: noise})
}
'
```

@@

bda <- webppl(
  program_code = paste(rsaUtils, rsaModel2, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T)
)

jsonlite::toJSON(data, pretty = T)

@@

filter(bda, Iteration == 1)

posterior.noise <- bda %>%
  filter(Parameter == "noise")%>%
  summarise(noise = mean(value))

posterior.predictive = bda %>%
  filter(Parameter != "noise") %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")

ggplot(posterior.predictive, aes(x = value))+
  geom_histogram(binwidth = .01)+
  facet_wrap(~Experiment+Change+Alignment, nrow = 2)

noisy.model <- posterior.predictive %>%
  mutate(Model="Noisy Model")%>%
  group_by(Model,Experiment,Change,Alignment)%>%
  multi_boot_standard(col = "value")

p.com <- bind_rows(noisy.model,pd)

ggplot(p.com, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Model)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)
